R Notebook

### 2022-05-30 code.Rmd
update files

Regression methods we will use: 
- full linear model (lm)
- subset selection (sub)
- ridge (ridge)
- lasso (lasso)
- elastic net (ela)
- principal components regression (pcr)

@@

performance <- function(df, modelName) {
  pf <- data.frame(modelName(df, 0))
  for (i in 1:9) {
    pf <- cbind(pf, modelName(df, i))
  }
  pf <- t(pf)
  print(pf)
  print(c(mean(pf[,1]), mean(pf[,2])))
}
```

@@

performance(houseSplit, linearModel)
performance(houseSplit, forwardModel)
performance(houseSplit, backwardModel)

@@

performance(houseSplit, ridgeModel)
#the ridge model has roughly the same RMSE, but slightly lower R2
performance(houseSplit, lassoModel)
#lasso has slightly lower RMSE, and a slightly higher R2 compared to ridge, but still lower than the linear model
performance(dummySplitWithResponse, elasticNetModel)
#elastic net has an even lower RMSE and a similar R2 compared with the previous two. Warning: this takes a longer time to run.
```

@@

performance(dummySplitWithResponse, PCRModel)
#This one has a higher R squared, but as a trade-off it also has high variance
```

>>>>

Regression methods we will use: 
- full linear model (lm)
- subset selection (forward, backward)
- ridge (ridge)
- lasso (lasso)
- elastic net (ela)
- principal components regression (pcr)

@@

performance <- function(df, modelName) {
  pf <- data.frame(modelName(df, 0))
  for (i in 1:9) {
    pf <- cbind(pf, modelName(df, i))
  }
  pf <- t(pf)
  print(c(mean(pf[,1]), mean(pf[,2])))
  return(c(mean(pf[,1]), mean(pf[,2])))
}
```

@@

#performance(houseSplit, linearModel)
#performance(houseSplit, forwardModel)
#performance(houseSplit, backwardModel)

@@

#performance(houseSplit, ridgeModel)
#the ridge model has roughly the same RMSE, but slightly lower R2
#performance(houseSplit, lassoModel)
#lasso has slightly lower RMSE, and a slightly higher R2 compared to ridge, but still lower than the linear model
#performance(dummySplitWithResponse, elasticNetModel)
#elastic net is between ridge and lasso in terms of both R2 and variance
```

@@

#performance(dummySplitWithResponse, PCRModel)
#This one has a higher R squared, but as a trade-off it also has high variance
```

```{r}
#compare the models

models <- data.frame(lm = performance(houseSplit, linearModel), forward = performance(houseSplit, forwardModel), backward = performance(houseSplit, backwardModel), ridge = performance(houseSplit, ridgeModel), lasso = performance(houseSplit, lassoModel), ela = performance(dummySplitWithResponse, elasticNetModel), pcr = performance(dummySplitWithResponse, PCRModel))

models
```
